Self Regulation Ontology Retest Analyses

### 2018-08-20 code/SRO_Retest_Analyses.Rmd
refactoring

```{r}
process_boot_df = function(df){
  df = df %>%
  drop_na() %>%
  mutate(dv = as.character(dv),
         icc = as.numeric(as.character(icc)),
         spearman = as.numeric(as.character(spearman)),
         pearson = as.numeric(as.character(pearson)),
         eta_sq = as.numeric(as.character(eta_sq)),
         sem = as.numeric(as.character(sem)),
         partial_eta_sq = as.numeric(as.character(partial_eta_sq)),
         omega_sq = as.numeric(as.character(omega_sq)),
         var_subs = as.numeric(as.character(var_subs)),
         var_ind = as.numeric(as.character(var_ind)),
         var_resid = as.numeric(as.character(var_resid)),
         F_time = as.numeric(as.character(F_time)),
         p_time = as.numeric(as.character(p_time)),
         df_time = as.numeric(as.character(df_time)),
         df_resid = as.numeric(as.character(df_resid)))
  return(df)}

demog_boot_df <- read.csv(gzfile(paste0(retest_data_path,'demog_boot_merged.csv.gz')))

>>>>

```{r}
demog_boot_df <- read.csv(gzfile(paste0(retest_data_path,'demog_boot_merged.csv.gz')))
